NumPy---Array Computation for Python

### 2019-12-12 paper.tex
Fix reference to improvement section

Over the past few years, with external financial support, NumPy has
seen renewed developer interest.  It is actively developed to meet the
needs of its community, including the addition of some fairly large
changes as outlined in Section~\ref{improvements}.

@@

\section*{Recent technical improvements}\label{improvements}

>>>>

Over the past few years, with external financial support, NumPy has
seen renewed developer interest.  It is actively developed to meet the
needs of its community, including the addition of some fairly significant
changes as outlined in the Recent technical improvements section below.

@@

\section*{Recent technical improvements}
